### 2022-04-04 preprint.tex
Deploy to GitHub Pages

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

@@

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\thispagestyle{empty}
{\Large\bfseries\sffamily Mismatch between IUCN range maps and species
interactions data illustrated using the Serengeti food web}
\vskip 5em

%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{3,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{4,5,6,‡}\quad %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{4,6,‡}

\textsuperscript{1}\,The University of British
Columbia\quad \textsuperscript{2}\,Computational Biodiversity Science
and Services\quad \textsuperscript{3}\,School of Natural and
Environmental Sciences, Newcastle
University\quad \textsuperscript{4}\,Université de
Montréal\quad \textsuperscript{5}\,Université de
Sherbrooke\quad \textsuperscript{6}\,Quebec Centre for Biodiversity
Science

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Gracielle T. Higino --- \texttt{graciellehigino@gmail.com}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill
\textbf{\sffamily Abstract: }Range maps are a useful tool to describe
the spatial distribution of species. However, they often need to be used
with caution, as they essentially represent a rough approximation of a
species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature, and species interactions data. More
precisely, we show that local networks built from those stacked range
maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers. We
use the well-described Serengeti food web of mammals and plants as our
case study, and provide updated range maps that take into account
food-web structure. In our analysis, most predator ranges were
restricted by the absence of herbivores. This restriction was sometimes
contradicted by GBIF occurrences, suggesting the mismatch can be due
either to the lack of information about ecological interactions or about
the geographical occurrence of preys. We finally discuss general
guidelines to help identify defective data among distributions and
interactions data, and we recommend this method as a valuable way to
assess weather the occurrence data that are being used, even if
incomplete, is ecologically accurate.
\vfill

\clearpage
\linenumbers
\pagestyle{normal}

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}

\geometry{includemp,
            letterpaper,
            top=1.2in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=1.95in,
            marginparsep=0.4in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangoutside,
             facing=yes,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}

@@

\setcounter{secnumdepth}{5}

\usepackage{titlesec}

\titleformat{\section}[block]
{\normalfont\large\sffamily}
{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}

\titleformat{\subsection}[runin]
{\normalfont\fontseries{b}\selectfont\filright\sffamily}
{\thesubsection.}{.5em}{}

\titleformat{\subsubsection}[runin]
{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}

\fancypagestyle{firstpage}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyfoot[R]{\footnotesize\ccby}
   \fancyfoot[L]{\footnotesize\sffamily\today}
}

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}

\noindent {\LARGE \textbf{\textsf{Mismatch between IUCN range maps and
species interactions data illustrated using the Serengeti food web}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{3,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{4,5,6,‡}, %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{4,6,‡}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{4,6,‡}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{4,6,‡}
\vskip 1em
\textsuperscript{1}\,The University of British
Columbia; \textsuperscript{2}\,Computational Biodiversity Science and
Services; \textsuperscript{3}\,School of Natural and Environmental
Sciences, Newcastle University; \textsuperscript{4}\,Université de
Montréal; \textsuperscript{5}\,Université de
Sherbrooke; \textsuperscript{6}\,Quebec Centre for Biodiversity
Science\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Gracielle T. Higino --- \texttt{graciellehigino@gmail.com}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
\noindent

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
range maps\\species interactions\\food web\\Serengeti\\}
}

\textbf{Abstract}:\,Range maps are a useful tool to describe the spatial
distribution of species. However, they often need to be used with
caution, as they essentially represent a rough approximation of a
species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature, and species interactions data. More
precisely, we show that local networks built from those stacked range
maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers. We
use the well-described Serengeti food web of mammals and plants as our
case study, and provide updated range maps that take into account
food-web structure. In our analysis, most predator ranges were
restricted by the absence of herbivores. This restriction was sometimes
contradicted by GBIF occurrences, suggesting the mismatch can be due
either to the lack of information about ecological interactions or about
the geographical occurrence of preys. We finally discuss general
guidelines to help identify defective data among distributions and
interactions data, and we recommend this method as a valuable way to
assess weather the occurrence data that are being used, even if
incomplete, is ecologically accurate.

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
